---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# groupMissingCount

<!-- badges: start -->

<!-- badges: end -->

The goal of `groupMissingCount` is to provide an easy-to-use function that counts missing values in each column of a dataframe grouped by a specified column. This package simplifies the process of analyzing missing data by groups using `dplyr` functions, making it ideal for data exploration and preliminary data analysis.

## Installation

You can install the development version of groupMissingCount from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2024/groupMissingCount")
```

## Examples

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column.

```{r example1}
library(groupMissingCount)
data(airquality)
# Count missing values by 'Month'
count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function.

```{r example2}
airquality |> count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples.

```{r example3}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
